%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead} % Job title
    {\href{https://sites.google.com/view/sathyabamacodingclub}{Developer Student Club[Google Initiative]}} % Organization
    {SathyabamaIST, chennai} % Location
    {February. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learning and building communities to make a difference in the way we learn.}
      \end{cvitems}
    }



  \cventry
    {Campassador} % Job title
    {Udacity} % Organization
    {SathyabamaIST, chennai} % Location
    {October. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Bringing opportunities to students and following the way Udacity changing the Education system}
      \end{cvitems}
    }
    
    
    
%---------------------------------------------------------
  \cventry
    {Software Engineer Intern \href{https://docs.google.com/spreadsheets/d/1dDO6C-KJg47RTLgM4caVn2qnPnrNxWdrVtkyauuFjb4/edit?usp=sharing}{(LogSheet)}} % Job title
    {Qube Cinema Technologies \href{https://www.qubecinema.com/}{(Webpage)} } % Organization
    {Chennai, TamilNadu} % Location
    {December. 2018 - Februray. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a service for receiving Issue Events information from GitHub Web-Hook and integrating it for an Internal tool.}
        \item {Designed and Developed an easy-to-use Command Line tool in python for enabling Issue Status Checks of repositories of an Organisation.}
        \item {Developed a feature for the server (Qube Wire Server) to Deauthorize the Theater/Partner appliance which utilizies Docker container, AWS stack, RabbitMQ, Redis. [Google Golang]}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Developer Intern} % Job title
    {Coffee Inc (Start-up company) \href{https://coffeeinc.in/}{(Webpage)}} % Organization
    {Chennai, TamilNadu} % Location
    {August. 2018 - October. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an Android Application for Events Organised by Coffee Inc. [Android Native Java]}
        \item {Built a Feature for an Existing Android Application for Registration Validation using QR Code.}
      \end{cvitems}
    }

%---------------------------------------------------------
  %%\cventry
   % {Freelance Penetration Tester} % Job title
    %{SAMSUNG Electronics} % Organization
    %{S.Korea} % Location
    %{Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
    %{
     % \begin{cvitems} % Description(s) of tasks/responsibilities
      %  \item {Conducted penetration testing on SAMSUNG KNOX, which is %solution for enterprise mobile security.}
      %  \item {Conducted penetration testing on SAMSUNG Smart TV.}
      %\end{cvitems}
      %%\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    %}

%---------------------------------------------------------
\end{cventries}
